\section{Arabic NLP Package}
\label{sec:arapy}

We have developed a simple python package for all of the utilities that we required to complete this research. As the software for Arabic NLP is somewhat difficult to acquire and apply, we believe that the utilities and wrappers we provide are greatly useful to anyone wanting to perform common NLP tasks in Arabic. We also hope to increase the utilization of Arabic word embeddings within the research community with this software. We call this open source package Arapy, and it will be available at \url{https://github.com/jordanking/arapy} upon completion of this work. 
\\
All preprocessing, normalization, and training processes outlined in this research utilize Arapy. The package itself utilizes various software packages and resources, including gensim, MADAMIRA, the Google Translate API, and the Big Huge Thesaurus API \cite{rehurek_lrec,pasha:2014,google:online,bhl:online}.
\\
Arapy includes many useful tools for simple NLP tasks that can be difficult when working with Arabic. The first is a module providing a MADAMIRA wrapper that provides access to the part-of-speech tagging, base phrase chunking, tokenization, and lemmatization features of MADAMIRA. There is also a wrapper providing various tools for training and evaluating Arabic word embeddings, primarily as a wrapper for gensim tools. Arapy also includes modules for Arabic text normalization, translation with Google Translate, simulation of an Arabic thesaurus with translation and the Big Huge Thesaurus API, and cleaning Arabic Wikipedia dumps. The main dependancies for this package are Java for MADAMIRA, the MADAMIRA jar and a license for MADAMIRA, gensim for word2vec model operations, a Google API key for translation, a Big Huge Thesaurus API key for thesaurus simulation. Complete documentation can be found in the repository at \url{https://github.com/jordanking/arapy}.
