\section{Conclusion and Future Directions}
\label{sec:conclusion}

This paper examines the training and evaluation of Arabic word embeddings. Furthermore it provides recommendations and tools to develop high quality Arabic word embeddings. The contributions of this work are as follows: 1) We perform a comparative empirical evaluation of Arabic and English word vectors using both a semantic similarity task and an analogy solving task. We show that standard parameters for English word embeddings can lead to poor Arabic word embeddings and that we find no universally optimal parameterization. 2) We present an empirical analysis identifying the parameters that are most effective for our tasks, identifying a set of best practices for training Arabic word embeddings. 3) We developed an open-source software package that provides easy access to important Arabic natural language processing tools. 
We have a few research directions that we believe would extend this work. We would like to expand our analysis with more training data and experiment with more parameter choices, which were heavily restricted by resources and time. Additionally, we would like to extend our results by training on different, larger data sources containing Arabic text. We would like to explore different applications for word embeddings and investigate if training parameters produce siginificantly different performances. Finally, we would like to continue to expand our NLP package, Arapy, to help other researchers perform Arabic NLP with ease.